---
title: 'Supporting Information'
subtitle: "``Transient top-down and bottom-up effects of resources pulsed to multiple trophic levels'' \\vspace*{6pt} \\linebreak \\emph{Ecology}"
date: ""
editor_options: 
  chunk_output_type: console
header-includes:
    - \usepackage{placeins}
    - \usepackage{cancel}
fontsize: 12pt
geometry: margin=1in,letterpaper
documentclass: article
graphics: true
tables: true
colorlinks: true
supplemental: true
mathspec: true
output:
    bookdown::pdf_document2:
        fig_caption: yes
        template: template.tex
        latex_engine: xelatex
        number_sections: false
        dev: cairo_pdf
        toc: false
author:
    - name: Matthew A. McCary
      nums: "1,*,§"
    - name: Joseph S. Phillips
      nums: "2,†,§"
    - name: Tanjona Ramiadantsoa
      nums: "2"
    - name: Lucas A. Nell
      nums: "2"
    - name: Amanda R. McCormick
      nums: "2"
    - name: Jamieson C. Botsch
      nums: "2"
affil:
    - name: "Department of Entomology, University of Wisconsin, Madison, WI 53706, USA"
      num: "1"
    - name: "Department of Integrative Biology, University of Wisconsin, Madison, WI 53706, USA"
      num: "2"
    - name: "Corresponding author.  Email: matt.mccary@gmail.com. Present address: School of Forestry and Environmental Studies, Yale University, New Haven, CT"
      num: "*"
    - name: "Present address: Department of Aquaculture and Fish Biology, Hólar University, Skagafjörður, Iceland"
      num: "†"
    - name: "Co-first authors"
      num: "§"
---




# Appendix S1: Supplementary Methods.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE,
                      fig.align = "center")
knitr::opts_knit$set(root.dir = normalizePath(".."))

# load packages
suppressPackageStartupMessages({
    library(mtf)
    library(tidyverse)
    library(grid)
    library(parallel)
    library(cowplot)
    library(egg)
})

# This sets plotting device on LAN computer:
if (!isTRUE(getOption('knitr.in.progress')) && file.exists(".Rprofile")) {
  source(".Rprofile")
}

# Clean captions
cc <- function(.x) {
    .x <- gsub("\n", "", .x)
    .x <- gsub("\\s+", " ", .x)
    return(.x)
}

parlist <- par_estimates %>%
        filter(V==1, H==1, X==1, iI == 10) %>%
        as.list()

V_gain <- function(V, D, aDV = parlist[["aDV"]]) {
    hD <- parlist[["hD"]]
    (aDV*D*V/(1 + aDV*hD*D)) / V
}

V_loss <- function(V, X, H, M, q, hM = parlist[["hM"]], .no_M_to_X = FALSE) {
    aX <- parlist[["aX"]]
    hX <- parlist[["hX"]]
    if (!.no_M_to_X) {
        Vl <- ((aX*V*X)/(1 + aX*hX*(V + H) + (aX * q)*hM*M)) / V
    } else {
        Vl <- ((aX*V*X)/(1 + aX*hX*(V + H))) / V
    }
    return(Vl)
}

H_gain <- function(P, H, aPH = parlist[["aPH"]]) {
    hP <- parlist[["hP"]]
    (aPH*P*H/(1 + aPH*hP*P)) / H
}

H_loss <- function(H, X, V, M, q, hM = parlist[["hM"]], .no_M_to_X = FALSE) {
    aX <- parlist[["aX"]]
    hX <- parlist[["hX"]]
    if (!.no_M_to_X) {
        Hl <- ((aX*H*X)/(1 + aX*hX*(V + H) + (aX * q)*hM*M)) / H
    } else {
        Hl <- (aX*H*X)/(1 + aX*hX*(V + H)) / H
    }
    return(Hl)
}

upper_levels <- c("detritivore", "herbivore", "predator")


```



## Section S1: Stability analysis

To determine the stability of the equilibrium state, we used the `deriv` function in 
R to numerically compute the Jacobian matrix, evaluated at the baseline parameter set
(i.e., using values from Table 1):

\begin{align*}
\left.
\begin{pmatrix}
    \frac{\partial F_I}{\partial I} & \frac{\partial F_I}{\partial D} & 
        \frac{\partial F_I}{\partial P} & \frac{\partial F_I}{\partial V} &
        \frac{\partial F_I}{\partial H} & \frac{\partial F_I}{\partial X} \\[1.5ex]
    \frac{\partial F_D}{\partial I} & \frac{\partial F_D}{\partial D} & 
        \frac{\partial F_D}{\partial P} & \frac{\partial F_D}{\partial V} &
        \frac{\partial F_D}{\partial H} & \frac{\partial F_D}{\partial X} \\[1.5ex]
    \frac{\partial F_P}{\partial I} & \frac{\partial F_P}{\partial D} & 
        \frac{\partial F_P}{\partial P} & \frac{\partial F_P}{\partial V} &
        \frac{\partial F_P}{\partial H} & \frac{\partial F_P}{\partial X} \\[1.5ex]
    \frac{\partial F_V}{\partial I} & \frac{\partial F_V}{\partial D} & 
        \frac{\partial F_V}{\partial P} & \frac{\partial F_V}{\partial V} &
        \frac{\partial F_V}{\partial H} & \frac{\partial F_V}{\partial X} \\[1.5ex]
    \frac{\partial F_H}{\partial I} & \frac{\partial F_H}{\partial D} & 
        \frac{\partial F_H}{\partial P} & \frac{\partial F_H}{\partial V} &
        \frac{\partial F_H}{\partial H} & \frac{\partial F_H}{\partial X} \\[1.5ex]
    \frac{\partial F_X}{\partial I} & \frac{\partial F_X}{\partial D} & 
        \frac{\partial F_X}{\partial P} & \frac{\partial F_X}{\partial V} &
        \frac{\partial F_X}{\partial H} & \frac{\partial F_X}{\partial X}
\end{pmatrix}
\right\rvert_{I = \hat{I},
              D = \hat{D},
              % P = \hat{P},
              % V = \hat{V},
              % H = \hat{H},
              \ldots,
              X = \hat{X}}
\text{.}
\end{align*}

\noindent where, for pool $Z$, $\frac{dZ}{dt} = F_Z(I, D, P, V, H, X)$ and 
$\hat{Z}$ is the equilibrium size.
Note that because this is nonlinear system, the Jacobian gives the linearization 
about the equilibrium.

The Jacobian at equilibrium was

\vspace*{1ex}


```{r stability-analysis}

pars <- par_estimates %>%
    filter(V == 1, X == 1, H == 1, iI == 10) %>%
    mutate(M = 0) %>% 
    dplyr::select(-V, -X, -H) %>% 
    rename_at(vars(ends_with("eq")), function(x) gsub("eq", "", x)) %>% 
    as.list()


##### Define functions for derivatives

deriv_exprs <- list(I = ~iI - aIP*I*P/(1 + aIP*hI*I) + (1 - lD)*muD*D - muI*I,
                    D = ~(1 - lP)*(muP + mP*P)*P + (1 - lV)*(muV + mV*V)*V + 
                        (1 - lH)*(muH + mH*H)*H + (1 - lX)*(muX + mX*X)*X + 
                        (1 - lM)*muM*M - aDV*D*V/(1 + aDV*hD*D) - muD*D,
                    P = ~aIP*I*P/(1 + aIP*hI*I) - aPH*P*H/(1 + aPH*hP*P) - (muP + mP*P)*P,
                    V = ~aDV*D*V/(1 + aDV*hD*D) - 
                        (aX*V*X)/(1 + aX*hX*(V + H) + (aX * q)*hM*M) -
                        (muV + mV*V)*V,
                    H = ~aPH*P*H/(1 + aPH*hP*P) - 
                        (aX*H*X)/(1 + aX*hX*(V + H) + (aX * q)*hM*M) -
                        (muH + mH*H)*H,
                    X = ~(aX*V*X + aX*H*X + 
                              (aX * q)*M*X)/(1 + aX*hX*(V + H) + (aX * q)*hM*M) -
                        (muX + mX*X)*X)

derivs <- map(deriv_exprs, 
              ~ deriv(.x,
                      c("I", "D", "P", "V", "H", "X"),
                      function(I, D, P, V, H, X, M,
                               iI, lD, lP, lV, lH, lX, lM,
                               muI, muD, muP, muV, muH, muX, muM, 
                               mP, mV, mH, mX, q,  
                               aIP, aDV, aPH, aX, hI, hD, hP, hX, hM){}))


##### Gradients at equilibrium

eq_gradients <- map(derivs, ~ do.call(.x, pars) %>% 
                        attributes() %>% 
                        .[["gradient"]])


##### Define jacobian

jac <- do.call(rbind, eq_gradients)
rownames(jac) <- colnames(jac)

# For printing:
jac_chr <- matrix(sprintf("$%.04f$", jac), 6, 6)
rownames(jac_chr) <- colnames(jac_chr) <- sprintf("$%s$", colnames(jac))
knitr::kable(jac_chr, "latex", booktabs = TRUE, escape = FALSE, align = 'r') %>% 
    gsub(pattern = "\\\\addlinespace\\n", replacement = "")

```

\vspace*{2ex}


We then computed the eigenvalues from this matrix to assess stability, where
negative values indicate stability.
The eigenvalues from the Jacobian are below:

\vspace*{1ex}

```{r stability-analysis-eigen-table}

eigen_analysis <- eigen(jac)
eigen_values <- eigen_analysis$values
leading_eigen <- max(Re(eigen_values))

# leading_eigen # leading eigenvalue is negative, so equilibrium is stable
# eigen_values # imaginary eigenvalues implies some kind of cyclic approach to equilibrium
# (but this gets complicated)

tibble(eigenvalue = sprintf("$%s$", paste(round(eigen_values, 4)))) %>% 
    knitr::kable(format = "latex", booktabs = TRUE, escape = FALSE) %>% 
    gsub(pattern = "\\\\addlinespace\\n", replacement = "")

```


\vspace*{2ex}

All of the eigenvalues of the Jacobian are negative, indicating that the
equilibrium is locally stable (in the sense that the system returns to equilibrium in
response to small perturbations near the equilibrium). 
There is one complex conjugate pair of eigenvalues, reflecting some kind of 
oscillatory or overcompensatory behavior in the approach to equilibrium (Hastings 2013),
which we see in the simulations in Fig. S1.
But these oscillations dampen out pretty quickly.




## Section S2: Simulating midges only going to predators or only to detritus


When midges only go to predators, we changed the following:


$$
\frac{dD}{dt} = {\color{red} \cancel{(1 - l) \mu_M M} } + (1 - l) \sum_{j \in \{ P,V,H,X \}}{ (\mu_j + m_j j) j } - 
    \frac{ a_D D V }{1 + a_D h_D D} - \mu_D D
$$


$\frac{dM}{dt}$ remains the same (i.e., it retains the $- \mu_M M$ term) so that 
midges do not build up indefinitely.



When midges only go to detritus, we changed the following:


\begin{align*}
\frac{dV}{dt} &= \frac{ a_D D V }{ 1 + a_D h_D D } - \frac{a_X V X }{ 1 + a_X h_X H + a_X h_X V {\color{red} \cancel{+ q a_X h_M M}} } - (\mu_V + m_V V) V \\
\frac{dH}{dt} &= \frac{ a_P P H }{ 1 + a_P h_P P } - \frac{a_X H X }{ 1 + a_X h_X H + a_X h_X V {\color{red} \cancel{+ q a_X h_M M}} } - (\mu_H + m_H H) H \\
\frac{dX}{dt} &= \frac{ (a_X V + a_X H {\color{red} \cancel{+ q a_X M}}) X }{ 1 + a_X h_X H + a_X h_X V {\color{red} \cancel{+ q a_X h_M M}} } - (\mu_X + m_X X) X \\
\frac{dM}{dt} &= i_{M(t)} {\color{red} \cancel{- \frac{q a_X M X }{ 1 + a_X h_X H + a_X h_X V + q a_X h_M M }}} - \mu_M M
\end{align*}





## Reference

Hastings, A. 2013. Population biology: concepts and models. Springer Science & Business
Media, New York, New York, USA.

